---
title: "Lab 4: Transformations for ANOVA"
subtitle: "STAT 242: Intermediate Statistics"
output: pdf_document
---

## Goals

The goal in this lab is to practice working with transformations for ANOVA.

## Loading packages

Here are some packages with functionality you may need for this lab.  Run this code chunk now.

```{r}
library(readr)
library(ggplot2)
library(gridExtra)
library(mosaic)
library(dplyr)
options("pillar.sigfig" = 10) # print 10 significant digits in summarize output
```

A gas chromatograph is an instrument that measures the amounts of various compounds contained in a sample by separating the various constituents.  The total number of counts recorded by the chromatograph is proportional to the amount of the compound present.

A calibration experiment was performed to see how the recorded counts from the chromatograph related to the concentration of a compound in a mixture and the flow rate through the chromatograph.  In this lab we will just look at the relationship between the concentration (explanatory variable) and the counts (response variable).

```{r}
chromatography <- read_csv("http://www.evanlray.com/data/sdm3/Chapter_29/Ch29_Chromatography.csv")
names(chromatography) <- c("concentration", "flow_rate", "counts")
chromatography %>%
  count(concentration)
```

**1. Make appropriate plots of the data: it would be nice to use a histogram or density plot, separately for each value of cylinders. A side-by-side boxplot is also useful. Also calculate the standard deviation for each group. Based on your plots and sample standard deviations, would it be appropriate to use an ANOVA model for these data?**

```{r}

```

**2. Find a transformation of the data so that the ANOVA model would be appropriate. Add a column to your data frame that implements this transformation.**

```{r}

```

**3. Report and interpret an estimate of the difference in the centers of the distributions of counts for the high concentration and the low concentration, as well as a 95% confidence interval for that difference.  You should be able to do this on the transformed scale and on the original scale (if appropriate).**

```{r}

```

**4. Conduct a test of the claim that the mean (transformed) count is the same for all three concentration levels. Make sure to state your hypotheses, run the appropriate R code, and interpret the strength of evidence offered by your p-value in context.**

```{r}

```
